---
title: "Gleb's Article Template"
format:
  gat-pdf:
    keep-tex: true  
  gat-html: default
author:
  - name: Gleb Ebert
    affiliations:
      - name: ETH Zurich
        department: D-USYS
        address: "Universitätsstrasse 16"
        city: Zurich
        country: Switzerland
        postal-code: 8092
    orcid: 0000-0002-7734-3824
    email: gleb.ebert@env.ethz.ch
    url: https://www.glebsite.ch/
abstract: |
  This document is only a demo explaining how to use the template.
keywords: [template, demo]
reference-section-title: References
bibliography: bibliography.bib  
---

# Demo of some features found in this demo journal template

## Shortcode demo {#sec-shortcode}

PDF are rendered using {{< latex >}} but it is best if one can use a Markdown syntax for cross format support.

`{{< latex >}}` used in source is a shortcode syntax where the shortcode is included in the extension folder `_extensions`

## Code chunk {#sec-chunks}

This format hide chunks by default as option has been set in `_extension.yml` file.

```{r}
#| prompt: true
# Loading some data but this chunk won't be shown.
data("quine", package = "MASS")
```

But you can set `echo` option to `true` locally in the chunk

```{r}
#| echo: true
m_pois <- glm(Days ~ (Eth + Sex + Age + Lrn)^2, data = quine, family = poisson)
summary(m_pois)
```


## Using references {.unnumbered}

This is how a reference looks like [@rcoreteamLanguageEnvironmentStatistical2022].

Differences between `gat-html` and `gat-pdf`: 

* For the HTML format, we are using Pandoc citeproc to include the bibliography. Here `reference-section-title` controls the title for the chapter that will be used.
* For the PDF format, `biblatex` is used by default and the bibliography is included with a title by the LaTeX template. 
